Applications of the Fresnel Integrals

### 2019-03-17 draft.tex
3.1 pictures
spellchecks

\subsection{Mathematical history}
The Fresnel integral and the related Euler spiral were discovered multiple times during history.  One of the first occurrances is according to \cite{Lev08} by J. Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.  In 1744, Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.  37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.  Fresnel discovers the curve in 1818 independently and successfully applies it to the diffraction on a slit \cite{Lev08}.  He is also able to compute a couple of values numerically.  In 1874 Cornu plotted the curve accurately and proposes it as a graphical means for computing diffraction problems.

@@

An object traveling on a circular path experiences a centripetral acceleration. The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path. This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.

In order to provide a smooth riding experience, much effort has been made in the history of railway construction. According to \cite{Lev08}, Mr. Gravatt was the first one who designed a sine curve around the year of 1828. Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree. In the year of 1880, Charles Crandall gives priority for the "true transition curve" to Ellis Holbrook in the Railroad Gazette. However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to "The Railway Transition Spiral" \cite{Tal99}:

@@

Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spiral independently. Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.

@@

\bibliographystyle{alphasorteprint}
\bibliography{bibliography.bib}
\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
\end{document}

>>>>

\subsection{Mathematical history}
The Fresnel integral and the related Euler spiral were discovered multiple times during history.  One of the first occurrences is according to \cite{Lev08} by J. Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.  In 1744, Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.  37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.  Fresnel discovers the curve in 1818 independently and successfully applies it to the diffraction on a slit \cite{Lev08}.  He is also able to compute a couple of values numerically.  In 1874 Cornu plotted the curve accurately and proposes it as a graphical means for computing diffraction problems.

@@

An object traveling on a circular path experiences a centripetal acceleration. The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path. This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.

In order to provide a smooth riding experience, much effort has been made in the history of railway construction. According to \cite{Lev08}, Mr. Gravatt was the first one who designed a sine curve around the year of 1828. Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree. In the year of 1880, Charles Crandall gives priority for the ``true transition curve'' to Ellis Holbrook in the Railroad Gazette. However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99}:

@@

Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spirals independently. Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.

@@

\bibliographystyle{alphasorteprint}
\bibliography{bibliography.bib}
%\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
\end{document}
